---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kendallknight <img src="man/figures/logo.svg" align="right" height="139" alt="" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/pachadotdev/kendallknight/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pachadotdev/kendallknight/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/pachadotdev/kendallknight/graph/badge.svg?token=kDP0pWmfRk)](https://codecov.io/gh/pachadotdev/kendallknight)
[![BuyMeACoffee](https://raw.githubusercontent.com/pachadotdev/buymeacoffee-badges/main/bmc-donate-yellow.svg)](https://www.buymeacoffee.com/pacha)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

## About

tldr; This package implements a different algorithm from the one implemented in
base R, and it reduces the complexity of the Kendall's correlation coefficient
from O(n^2) to O(n log n) resulting in a runtime of nano seconds or minutes
instead of minutes or hours. This package is written in C++ and uses cpp11 to
export the functions to R. See the vignette for the mathematical details.

If this software is useful to you, please consider donating on
[Buy Me A Coffee](https://buymeacoffee.com/pacha). All donations will
be used to continue improving `kendallknight`.

## Installation

You can install the development version of kendallknight like so:

``` r
remotes::install_github("pachadotdev/kendallknight")
```

## Examples

See the documentation: https://pacha.dev/kendallknight.

# Benchmarks

We tested the `kendallknight` package against the base R implementation of the
Kendall correlation using the `cor` function with `method = "kendall"` for
randomly generated vectors of different lengths. The results are shown in the
following table:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(dplyr)
library(tidyr)

benchmarks <- readRDS("dev/benchmarks_all.rds") %>%
  mutate(expression = ifelse(expression == "kendall_cor(x, y)", "kendallknight", "base R"))

benchmarks %>%
  select(expression, nobs, median) %>%
  pivot_wider(names_from = expression, values_from = median) %>%
  arrange(nobs) %>%
  rename(
    `Number of observations` = nobs,
    `kendallknight median time (s)` = kendallknight,
    `base R median time (s)` = `base R`
  ) %>%
  # format nobs as thousands
  mutate(`Number of observations` = scales::comma(`Number of observations`)) %>%
  kable(digits = 3)

benchmarks %>%
  select(expression, nobs, mem_alloc) %>%
  pivot_wider(names_from = expression, values_from = mem_alloc) %>%
  arrange(nobs) %>%
  rename(
    `Number of observations` = nobs,
    `kendallknight memory allocation (MB)` = kendallknight,
    `base R memory allocation (MB)` = `base R`
  ) %>%
  # format nobs as thousands
  mutate(`Number of observations` = scales::comma(`Number of observations`)) %>%
  kable(digits = 3)
```

In order to avoid distorted results, we used the `bench` package to run the
benchmarking tests in a clean R session and in the Niagara supercomputer
cluster that, unlike personal computers, will not distort the test results due
to other processes running in the background (e.g., such as automatic updates).

# Testing

The package uses `testthat` for testing [@wickham2011]. The included tests are
exhaustive and covered the complete code to check for correctness comparing with
the base R implementation, checking corner cases, and forcing errors
by passing unusable input data to the user-visible functions.

## Code of Conduct

Please note that the kendallknight project is released with a
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
